\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-02 doc/sw-system.tex
Tweaks to tex, added PDFs back in for easier viewing

The mathematics of the offline inference are presented elsewhere (in
preparation). Here we briefly note that we maximize the joint posterior
probability distribution for all the model parameters (some 66,000 confusion
matrix elements and 430,000 subject probabilities) with a simple
expectation-maximisation algorithm. This procedure takes approximately the same
CPU time as the online analysis, because no matrix inversions are required in
the algorithm. The algorithm scales well and is actually faster than the online
analysis with the larger stage 1 dataset. The expectation-maximisation
algorithm is robust to initial starting parameters in, e.g., initial Agent
confusion matrix elements and Subject probabilities. The plots in
\Sref{sec:results:sample} show the difference in performance between the online
and offline analyses.

>>>>

The mathematics of the offline inference are presented elsewhere (in
preparation). Here we briefly note that we maximize the joint posterior
probability distribution for all the model parameters (some 66,000 confusion
matrix elements and 430,000 subject probabilities) with a simple
expectation-maximisation algorithm. This procedure takes approximately the
same CPU time as the stage 2 online analysis, because no matrix inversions are
required in the algorithm. The algorithm scales well and is actually faster
than the online analysis with the larger stage 1 dataset. The
expectation-maximisation algorithm is robust to initial starting parameters
in, e.g., initial Agent confusion matrix elements and Subject probabilities.
The plots in \Sref{sec:results:sample} show the difference in performance
between the online and offline analyses.
